State of the Practice for Lattice Boltzmann Method Software

### 2022-03-03 StateOfPractice/Papers/LatticeBoltz_SOP-arXiv/LatticeBoltz_SOP.tex
Edits to concluding remarks

	\item[Reproducibility] Once re-runnability and repeatability are achieved,
	the next step is reproducibility.  Current work by LBM developers on
	reproducibility is discussed in Section~\ref{SecReproducibility}.  The
	proposed goal for the future is for all results to be reproducible, which
	means documenting dependencies, platforms, parameter values and input files.
	The data and scripts behind the graphs should be published
	\citep{BenureauAndRougier2017}.

@@

We analyzed the state of the practice of software development in the Lattice
Boltzmann Methods software domain by quantitatively and qualitatively measuring,
and comparing, 24 software packages along quality attributes. The software
qualities that were assessed in this report are listed in
Section~\ref{softwarequalities}. A methodology for assessing the state of the
practice of software development in scientific domains was presented. Domain
packages were assessed to answer the software development related research
questions listed in Section~\ref{secIntro} to understand how software quality is
impacted by software development choices, including principles, processes, and
tools. Software developers were interviewed to identify development pain points,
and to identify how software quality is ensured. Quantitative data was used to
rank the software packages using the AHP. The ranking designations were compared
with rankings from the software development community, and we found that many of
our top 10 ranked packages are ranked highly by a domain expert. Recommendations
for improving software along quality metrics were made... The findings of this
report can be used to guide future development of research software,
specifically along quality attributes, and to reduce software quality failures.

@@

@@

Include a table that summarizes the top 4 projects for each quality, but an
asterisk if still alive.

@@

- value of tools to enforce good behaviour of developers, like R, like MOOSE
infrastructure

- introduce the idea of using our measurement template as a checklist, instead
of, or in addition to other checklists - cite the other checklists
\citep{SchlauchEtAl2018, BrettEtAl2021, vanGompelEtAl2016}, \href{Software
Sustainability Institute Online
Form}{https://docs.google.com/forms/d/e/1FAIpQLSf0ccsVdN-nXJCHLluJ-hANZlp8rDKgprJa0oTYiLZSDxh3DA/viewform}

- mention flake8 for Python?

- mention \href{https://joss.theoj.org/}{The Journal of Open Source Software}

- reproducibility - can point to the PiccoloAndFrampton2016 paper

- AlNoamanyAndBorghi2018 lists the most popular languages, Python is number 1

@@

- ``unique challenges of scientific research (e.g., the frequent and unforeseen
changes in requirements ...)'' \citep{PintoEtAl2018}. We can point out that in
the future this viewpoint could change and why.  Not really a unique challenge.
Cite Smith 2016?

>>>>

	\item[Reproducibility] Once re-runnability and repeatability are achieved,
	the next step is reproducibility.  Current work by LBM developers on
	reproducibility is discussed in Section~\ref{SecReproducibility}.  The
	proposed goal for the future is for all results to be reproducible, which
	means documenting dependencies, platforms, parameter values and input files.
	The data and scripts behind the graphs should be published
	\citep{BenureauAndRougier2017}.  Some tools and techniques for computational
	reproducibility are summarized in \citet{PiccoloAndFrampton2016}.

@@

To potentially improve the quality of LBM software, and help future users select
the right package, our goal was to analyze the current state of LBM software
development, including determining how well current best practices are followed
and finding pain points for developers.  We compared the state of the practice
for LBM software to the development practices recommended and employed for
research software in general. To improve the quality of LBM software we looked
for examples where developers have been successful so that we can share these
with the LBM community, and with the broader research software community.  We
also aimed to identify potential approaches for mitigating the identified pain
points in the future.

Our methodology involved the following steps: i) Identify a list of 45 candidate
software packages; ii) Filter the list to a length of 24 packages; iii) Collect
repository related data on each software package, like number of stars, number
of open issues, number of lines of code; iv) Fill in the measurement template
(the template consists of 108 questions to assess 9 qualities (installability,
correctness/verifiability, reliability, robustness, usability, maintainability,
reusability, understandability, and visibility/transparency)   The repository
data is collected by filling in a 108 question measurement template, which
requires installing the software on a VM, running simple tests (like completing
the getting started instructions (if present)), and searching the code,
documentation and test files.; v) Rank the software using the Analytic Hierarchy
Process (AHP); vi) Interview developers (the interview consists of 20 questions
and takes about an hour); and, vii) Conduct a domain analysis. The collected
data is analyzed by: a) comparing the ranking by best practices against the
ranking by popularity; b) comparing artifacts, tools and processes to current
research software development guidelines; and, c) exploring pain points.

Table~\ref{topperformerstable} summarizes the top 5 performers for each of the qualities that we assessed.

Comparison to community.

Comparison of artifacts.

Comparison of tools.

Comparison of processes.

Developer pain Points

Lessons from developers

@@

Future work

@@

@@

@@
